Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-03-26 analysis/paper/paper.Rmd
Writing in progress.

```{r method-tbl}
tbl2 <- "Projection method|Sample type|Sample density (pts/km^2^)|Resolutions
MST|Regular|1|1 ha and 100 ha
MST|Regular|10|1 ha and 100 ha
MST|Random|1|1 ha and 100 ha
MST|Random|10|1 ha and 100 ha
MST|Centroid|N/A|1 ha and 100 ha
ILCP|Regular|10|1 ha 
Hardy QGIS|N/A|~9|1 ha
Cutblocks only|N/A|N/A|1 ha

>>>>

```{r method-tbl}
tbl2 <- "Projection method|Sample type|Sample density (pts/km^2^)|Resolutions
MST grade penalty & simple cost|Regular|1|1 & 100 ha
MST grade penalty & simple cost|Regular|10|1 & 100 ha
MST grade penalty & simple cost|Random|1|1 & 100 ha
MST grade penalty & simple cost|Random|10|1 & 100 ha
MST grade penalty & simple cost|Centroid|N/A|1 & 100 ha
ILCP grade penalty & simple cost|Regular|10|1 ha 
Hardy QGIS|N/A|~9|1 ha
Cutblocks only|N/A|N/A|1 ha
